Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-03-17 writeup/gz_hubble_data.tex
Tables for main sample, SDSS single and coadd

\usepackage{epsfig}
\usepackage{color,soul}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{deluxetable}
\bibliographystyle{mn2e}

@@

\centering
%\rotate
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{GZH redshifts by survey} 
\label{tab:redshifts}
\tabletypesize{\scriptsize}
\tablehead{
 &   
\multicolumn{2}{c}{\underline{Griffith}} &
\multicolumn{3}{c}{\underline{3DHST}} &
\multicolumn{2}{c}{\underline{MUSYC}} &
\multicolumn{1}{c}{\underline{UltraVISTA}}&
\multicolumn{2}{c}{\underline{Total}} 
\\
\colhead{Survey} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{grism-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{photo-z} & 
\colhead{with redshift} &
\colhead{in survey}
}
\small
\startdata
%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373  & 8,507\\
COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020 & 92,808 \\
GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743  & 9,304\\
GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328  & 12,030 \\
GOODS-S  & 1,080  & 4      & 327 & 1,348 &  281    & 816   & 1,184 & 0       & 5,040  & 10,284 \\
SDSS     & 0      & 0      & 0   &  0    &  0      & 0     & 0     & 0       & 37,545 & 51,861  \\
\hline
Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794\\
\enddata
\end{deluxetable}

@@

We compiled redshifts from a variety of sources to include in the GZH catalog. For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tab:catalog}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.

For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift. We first prioritize spectroscopic redshifts; these are provided in the Griffith, 3DHST, and MUSYC catalogs. If a high quality spec-z exists in the Griffith catalog we use that, else 3DHST, else MUSYC. We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference. If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (Griffith, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error. Table~\ref{tab:redshifts} shows the results of this selection.

@@

\subsection{Results of $\zeta$ approach}

@@

The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and $\pfeatures$ a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of z, $\mu$, and $\pfeatures$. To define this smooth space, we use a convex hull method to enclose the correctable and uncorrectable \ferengi{} galaxies is z-$\mu$-$\pfeatures$ space. Due to scatter, the boundaries of the resulting hulls overlap. The boundaries are then adjusted until the contamination from both groups is minimized. We use the resulting hulls to define the correctable and uncorrectable regions for categorizing the Hubble galaxies. The results of this method and final categorization of the Hubble sample is displayed in Table~\ref{hubble_debiasable}. We find that of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.

@@

\begin{itemize}
\item talk about where the Hubble sample falls in this space, reference table \ref{hubble_debiasable} 
\item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
\item show some data for $\pbar$, determine or justify why we won't debiase them  
\end{itemize}

\begin{table*}
\caption{Breakdown of what we can correct out of the GZH data, by sample.  \emph{updated from 3-8-16: Switching to full depth for all GOODS data. Shallow depth information in appendix.}\label{hubble_debiasable}}
\begin{tabular}{lrrrrrrrr}
\hline\hline
                                  & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S         & SDSS    & Total \\
\hline
Correctable                        & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
Uncorrectable                      & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
No Correction Needed ($z \le 0.3$) & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
NEI                                & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
No Redshift Information            & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
Total                              & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
\hline\hline
\end{tabular}
\end{table*}

@@

\tabletypesize{\scriptsize}
\begin{deluxetable}{lrrllcrrrrrr|c}
\centering
\rotate
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications} 
\label{tab:catalog}
\tabletypesize{\scriptsize}
\tablehead{
 &  &   &  &  
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\dots$}
\\
\colhead{OBJNO} & 
\colhead{RA} & 
\colhead{DEC} & 
\colhead{Imaging} & 
\colhead{Correctable Category} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{best} &
\colhead{}
}
\small
\startdata
13035128            & 214.99  & 53.02    & AEGIS   &  correctable  		&  121 &  0.46 &  0.50 & 0.12 & 0.14 & 0.73 & 0.12 \\
13035131            & 215.01  & 53.02    & AEGIS   &  nei           		&  134 &  0.61 &  0.65 & 0.20 &      &      & 0.65 \\
    ...             & ...     & ...      &  ...    &  ...              		&  ... & ...   &  ...  & ...  & ...  & ...  & ...  \\
20055697            & 150.52  & 2.09     & COSMOS  &  correctable   		&  52  &  0.52 &  0.55 & 0.38 & 0.55 & 0.81 & 0.38  \\
20055698            & 150.50  & 2.09     & COSMOS  &  uncorrectable 		&  31  &  0.61 &  0.70 & 0.47 & 0.47 & 0.80 & 0.70 \\
    ...             & ...     & ...      &  ...    &  ...              		&  ... & ...   &  ...  & ...  & ...  & ...  & ...  \\
90021901            & 53.29   & -27.85   & GEMS    &  correctable   		&  131 &  0.21 &  0.21 & 0.15 & 0.14 & 0.35 & 0.15 \\
90021903            & 53.34   & -27.83   & GEMS    &  $z<0.3$         		&  142 &  0.78 &  0.80 & 1.04 &      &      & 0.80 \\
    ...             & ...     & ...      &  ...    &  ...              		&  ... & ...   &  ...  & ...  & ...  & ...  & ...  \\
GDS\_N\_2333        & 189.02  & 62.12    & GOODS-N & $\rm nei\_needs\_redshift$ &  40  &  0.33 &  0.33 & 0.87 &      &      & 0.33 \\
GDS\_S\_3132        & 53.04   & -27.71   & GOODS-S & uncorrectable              &  40  &  0.83 &  0.83 & 0.45 & 0.38 & 0.85 & 0.83 \\
    ...             & ...     & ...      &  ...    &  ...              		&  ... & ...   &  ...  & ...  & ...  & ...  & ...  \\
587731173843665742  & 315.58  & 0.25     & SDSS    & $z<0.3$                    &  48  & 0.79  & 0.89  & 1.23 &      &      & 0.89 \\
587731173843730515  & 315.61  & 0.30     & SDSS    & $z<0.3$                    &  53  & 0.68  & 0.75  & 1.06 &      &      & 0.75 \\

\enddata
\tablecomments{Full version is online at some website, here are 10 rows out of 181,101 in the full version.}
\end{deluxetable}

@@

Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2. 
\section{Using the Catalog}
\label{sec:cookbook}
Include cookbook for selecting morphologies. 
\section{Analysis}

>>>>

\usepackage{epsfig}
\usepackage{color,soul}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{deluxetable}
\usepackage{url}
\bibliographystyle{mn2e}

@@

\centering
%\rotate
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{GZH redshifts by survey} 
\label{tbl:redshifts}
\tabletypesize{\scriptsize}
\tablehead{
 &   
\multicolumn{2}{c}{\underline{Griffith}} &
\multicolumn{3}{c}{\underline{3DHST}} &
\multicolumn{2}{c}{\underline{MUSYC}} &
\multicolumn{1}{c}{\underline{UltraVISTA}}&
\multicolumn{2}{c}{\underline{Total}} 
\\
\colhead{Survey} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{grism-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{photo-z} & 
\colhead{with redshift} &
\colhead{in survey}
}
\small
\startdata
%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373  & 8,507\\
COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020 & 92,808 \\
GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743  & 9,304\\
GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328  & 12,030 \\
GOODS-S  & 1,080  & 4      & 327 & 1,348 &  281    & 816   & 1,184 & 0       & 5,040  & 10,284 \\
SDSS     & 0      & 0      & 0   &  0    &  0      & 0     & 0     & 0       & 37,545 & 51,861  \\
\hline
Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794\\
\enddata
\end{deluxetable}

@@

We compiled redshifts from a variety of sources to include in the GZH catalog. For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.

For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift. We first prioritize spectroscopic redshifts; these are provided in the Griffith, 3DHST, and MUSYC catalogs. If a high quality spec-z exists in the Griffith catalog we use that, else 3DHST, else MUSYC. We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference. If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (Griffith, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error. Table~\ref{tbl:redshifts} shows the results of this selection.

@@

\subsection{Results of $\zeta$ approach}\label{ssec:zeta_results}

@@

The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and $\pfeatures$ a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of z, $\mu$, and $\pfeatures$. To define this smooth space, we use a convex hull method to enclose the correctable and uncorrectable \ferengi{} galaxies is z-$\mu$-$\pfeatures$ space. Due to scatter, the boundaries of the resulting hulls overlap. The boundaries are then adjusted until the contamination from both groups is minimized. We use the resulting hulls to define the correctable and uncorrectable regions for categorizing the Hubble galaxies. The results of this method and final categorization of the Hubble sample is displayed in Table~\ref{tbl:hubble_debiasable}. We find that of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.

@@

\begin{itemize}
\item talk about where the Hubble sample falls in this space, reference table \ref{tbl:hubble_debiasable} 
\item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
\item show some data for $\pbar$, determine or justify why we won't debiase them  
\end{itemize}

\begin{table*}
\caption{Breakdown of what we can correct out of the GZH data, by sample.  \emph{updated from 3-8-16: Switching to full depth for all GOODS data. Shallow depth information in appendix.}\label{tbl:hubble_debiasable}}
\begin{tabular}{lcrrrrrrr}
\hline\hline
                                   & Correction type & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S    & SDSS    & Total \\
\hline
Correctable                        & 0               & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
Uncorrectable                      & 1               & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
No Correction Needed ($z \le 0.3$) & 2               & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
NEI                                & 3               & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
No Redshift Information            & 4               & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
Total                              &                 & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
\hline\hline
\end{tabular}
\end{table*}

@@

\tabletypesize{\scriptsize}
\begin{deluxetable}{lllllcrllllll|c}
\centering
\rotate
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for AEGIS, COSMOS, GEMS, and GOODS images} 
\label{tbl:catalog}
\tabletypesize{\scriptsize}
\tablehead{
 & & & RA & dec  &  
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{J2000} & 
\colhead{J2000} & 
\colhead{Correction$^{1}$} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{}
}
\small
\startdata
AHZ100002g  & 10010842  & AEGIS             &          &            & 0        & 948       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226    \\
AHZ100002h  & 10010870  & AEGIS             &          &            & 4        & 429       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$      \\
$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
AHZ20004kd  & 20014731  & COSMOS            &          &            & 3        & 185       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$      \\
AHZ20004ke  & 20014732  & COSMOS            &          &            & 2        & 149       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$      \\
$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
AHZ400043g  & 90022729  & GEMS              &          &            & 1        & 400       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800    \\
AHZ4000416  & 90022735  & GEMS              &          &            & 1        & 463       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727    \\
$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH &          &            & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496    \\
AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH &          &            & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669    \\
$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH &          &            & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548    \\
AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH &          &            & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287    \\
\enddata
\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible. 0~=~correctable, 1~=~uncorrectable ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrectable (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrectable (no galaxy redshift available).}
\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}. The complete version includes data for 118,425~galaxies and morphological information for all tasks in the tree. A subset of the information is shown here to illustrate form and content.}
\end{deluxetable}

% Why are some values negative?
% Why are most of the full-depth GOODS weighted fractions identical to the raw fractions?

\tabletypesize{\scriptsize}
\begin{deluxetable}{lllllcrllll|c}
\centering
\rotate
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for SDSS Stripe 82 single-epoch images} 
\label{tbl:stripe82_single}
\tabletypesize{\scriptsize}
\tablehead{
 & & & RA & dec  &  
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{4}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{J2000} & 
\colhead{J2000} & 
\colhead{Correction$^{1}$} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{}
}
\small
\startdata
AHZ5000001  &   587730845812064684  &   SDSS    &   &   &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594   \\
AHZ5000002  &   587730845812065247  &   SDSS    &   &   &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651   \\
AHZ5000003  &   587730845812196092  &   SDSS    &   &   &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043   \\
AHZ5000004  &   587730845812196825  &   SDSS    &   &   &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605   \\
AHZ5000005  &   587730845812524122  &   SDSS    &   &   &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810   \\
AHZ5000006  &   587730845812654984  &   SDSS    &   &   &     2 &   42  &   0.5	    &    0.542  &   0.680   &   0.541   \\
AHZ5000007  &   587730845812655541  &   SDSS    &   &   &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525   \\
AHZ5000008  &   587730845812720365  &   SDSS    &   &   &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839   \\
AHZ5000009  &   587730845812720640  &   SDSS    &   &   &     4 &   43  &   0.0	    &    0.0    &   0.0	    &   0.0	    \\
AHZ500000a  &   587730845812720699  &   SDSS    &   &   &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477   \\
$\ldots$    & $\ldots$  & $\ldots$  & $\ldots$  & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$ \\
\enddata
\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible. 0~=~correctable, 1~=~uncorrectable ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrectable (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrectable (no galaxy redshift available).}
\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}. The complete version includes data for 21,522~galaxies and morphological information for all tasks in the tree. A subset of the information is shown here to illustrate form and content.}
\end{deluxetable}

\tabletypesize{\scriptsize}
\begin{deluxetable}{lllllcrllll|c}
\centering
\rotate
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for SDSS Stripe 82 coadded images} 
\label{tbl:stripe82_coadd}
\tabletypesize{\scriptsize}
\tablehead{
 & & & RA & dec  &  
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{4}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{J2000} & 
\colhead{J2000} & 
\colhead{Correction$^{1}$} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{}
}
\small
\startdata
AHZ6000001  & 8647474690312306978   &   SDSS    &   &   &    4  & 40  & 0.275   &    0.289  &   0.762   &   0.289   & \\
AHZ6000002  & 8647474690312307154   &   SDSS    &   &   &    2  & 43  & 0.605   &    0.634  &   0.858   &   0.635   & \\
AHZ6000003  & 8647474690312307877   &   SDSS    &   &   &    2  & 51  & 0.608   &    0.627  &   0.906   &   0.627   & \\
AHZ6000004  & 8647474690312308301   &   SDSS    &   &   &    4  & 52  & 0.038   &    0.038  &   0.723   &   0.038   & \\
AHZ6000005  & 8647474690312308318   &   SDSS    &   &   &    2  & 44  & 0.614   &    0.632  &   0.776   &   0.631   & \\
AHZ6000006  & 8647474690312308880   &   SDSS    &   &   &    2  & 36  & 0.667   &    0.683  &   0.901   &   0.683   & \\
AHZ6000007  & 8647474690312372644   &   SDSS    &   &   &    4  & 48  & 0.646   &    0.674  &   1.145   &   0.674   & \\
AHZ6000008  & 8647474690312372789   &   SDSS    &   &   &    4  & 45  & 0.489   &    0.571  &   0.964   &   0.570   & \\
AHZ6000009  & 8647474690312372931   &   SDSS    &   &   &    4  & 47  & 0.553   &    0.587  &   0.926   &   0.587   & \\
AHZ600000a  & 8647474690312373190   &   SDSS    &   &   &    4  & 47  & 0.574   &    0.559  &   1.008   &   0.559   & \\
$\ldots$    & $\ldots$  & $\ldots$  & $\ldots$  & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$ \\
\enddata
\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible. 0~=~correctable, 1~=~uncorrectable ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrectable (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrectable (no galaxy redshift available).}
\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}. The complete version includes data for 30,339~galaxies and morphological information for all tasks in the tree. A subset of the information is shown here to illustrate form and content.}
\end{deluxetable}

@@

Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2. 
\section{Using the catalog}
\label{sec:cookbook}
Include cookbook for selecting morphologies. 
\section{Analysis}
